### 2019-12-26 Sections/cryptowars.tex
quantum enigma machine + bib

This led to the proposal for \textit{quantum Enigma machines}\footnote{The Enigma machine\index{Enigma machines} was the classical cryptosystem employed by the Germans during World War 2 for military and intelligence communication.} \cite{bib:LloydEnigma}. The protocol is shown in Fig.~\ref{fig:enigma}.

@@

Here Alice and Bob share a short secret-key $k$ of length $m$, and wish to communicate a message $j$ of length $n$. The secret-key might be established via conventional QKD. First off, they agree upon a set of Haar-random unitaries\index{Haar measure}, $\{\hat{U}_k\}$, associating one with each of the possible $2^m$ keys. This needn't be performed in secret. Alice then encodes her message into the state $\ket{j}$. Her encryption operation is to apply $\hat{U}_k$ to this state according to Alice and Bob's shared secret-key, yielding the encoded state,
\begin{align}
\ket{j}_k=\hat{U}_k\ket{j},
\end{align}
which Bob is easily able to decrypt using the inverse unitary,
\begin{align}
\hat{U}_k^\dag\ket{j}_k=\ket{j}.
\end{align}

To characterise the security of the scheme, we first note that in the absence of knowing the key or message, and assuming all $j$ and $k$ are equally likely, Eve observes the mixed state,
\begin{align}
\hat\rho_\mathrm{enc} &= \frac{1}{2^{m+n}} \sum_{j,k} \hat{U}_k\ket{j}\bra{j}\hat{U}^\dag_k \nonumber\\
&= \frac{1}{2^{m+n}} \sum_{j,k} \ket{j}_k\bra{j}_k.
\end{align}
The security can now be quantified in terms of the accessible information\footnote{The accessible information is the maximum of the mutual information between Alice's input states and measurements performed on the encoded state by Eve.}\index{Accessible information} between this state and the plaintext state, which can be upper-bounded as,
\begin{align}
	I_c \leq n + \frac{1}{2^m}\max_{\ket\phi}\sum_{j,k} |\braket{ \phi|j}_k|^2 \log |\braket{ \phi|j}_k|^2.
\end{align}
It was shown that this quantity can be made arbitrarily small with key-size scaling as,
\begin{align}
m=O(\log n),
\end{align}
which represents very frugal requirements in key-size versus message length. They further showed that the scheme can be made robust against noise and loss.

Note that the security of the scheme is information-theoretic\index{Information-theoretic!Security}, and does not make any assumptions about computational security\index{Computational!Security} (except we require the assumption that Eve has finite quantum memory). Thus, this represents a strong form of quantum private-key cryptography, requiring only very short keys compared to message length that may be reused.

However, the scheme is very challenging to implement on a large scale over long distances. Consider an optical implementation, where the message is photonically encoded. Now the scheme represents a complex, multi-mode, generalised Mach-Zehnder interferometer\index{Mach-Zehnder (MZ) interference}, meaning that the channel between Alice and Bob, who might be far apart, must be interferometrically stabilised\index{Interferometric!Stability} (Sec.~\ref{sec:opt_stab}) on the order of the photons' wavelength (hundreds of nanometers for optical frequencies), which is extremely challenging over long distances.

@@

% \subsection{Quantum random number generation}

% \subsection{Quantum data locking - the quantum enigma machine}

>>>>

This led to the proposal for \textit{quantum Enigma machines}\footnote{The Enigma machine\index{Enigma machines} was the classical cryptosystem employed by the Germans during World War 2 for military and intelligence communication.} \cite{bib:LloydEnigma}, based on the phenomenon of quantum data locking \cite{DiVin}. The protocol is shown in Fig.~\ref{fig:enigma}.

@@

Quantum data locking is a uniquely to quantum phenomenon, and presents one of the widest separations between the classical and quantum information theory \cite{bib:guha2014enigma}.
Quantum data locking occurs when the accessible information about a classical message encoded into a quantum state decreases by a much larger amount, when ``locked" with a much smaller key.

% Shannon proved that such a locking effect is impossible classically.

Here Alice and Bob share a short secret-key of length $K$, and wish to communicate a message $M$ of length $n-$bits. The secret-key is assumed to be unconditionally secure, and can be established via conventional QKD. First off, they agree upon a set of $K$ Haar-random unitaries (but it is sufficient to consider 2-designs) \index{Haar measure}, $\{\hat{U}_k\}$, associating one with each of the possible $K$ keys. The set of $\{\hat{U}_k\}$ unitaries need not be a secret.

Alice then encodes her message into the state $\ket{j}$. Her encryption operation is to apply $\hat{U}_k$ to this state according to Alice and Bob's shared secret-key.

\begin{align}
\ket{j}_k=\hat{U}_k\ket{j},
\end{align}
which Bob is easily able to decrypt using the inverse unitary,
\begin{align}
\hat{U}_k^\dag\ket{j}_k=\ket{j}.
\end{align}

To characterise the security of the scheme, we first note that in the absence of knowing the key or message, and assuming all $j$ and $k$ are equally likely, Eve observes the mixed state,

\begin{align}\label{eq:ghwoirsfjnk}
 \hat \rho_\text{enc}= \frac{1}{2^n} \sum_{j=1}^{2^n} \ket{j}_A\bra{j} \otimes \frac{1}{K}\sum_{k=1}^K U_k\ket{\psi_j}_E\bra{\psi_j}U_k^\dagger   .
\end{align}

The security can now be quantified in terms of the accessible information
\footnote{The accessible information is the maximum of the mutual information between Alice's input states and measurements performed on the encoded state by Eve.}\index{Accessible information} between this state and the plaintext state, which can be upper-bounded as \cite{lupo2015NJP,lupo2014pra},
% 
% 
\begin{align}
	I_c \leq n + \frac{1}{2^n}\max_{\ket\phi}\sum_{j,k} |\braket{ \phi|j}_k|^2 \log |\braket{ \phi|j}_k|^2.
\end{align}
It was shown that this quantity can be made arbitrarily small with key-size scaling as,
\begin{align}
m=O(\epsilon\log n),
\end{align}
\noindent for an $\epsilon$ that can be made arbitrarily small, given $\log K \sim \log{(1/\epsilon)}$, therefore the key size is exponentially smaller than the length of the message. Thus, we have an encryption scheme that requires very frugal requirements in key-size versus message length. It is further showed that such a scheme can be made robust against noise and loss \cite{lupo2014pra, lupo2015NJP}.

Note that the security of the scheme is information-theoretic\index{Information-theoretic!Security}, and does not make any assumptions about computational security\index{Computational!Security} (except we require the assumption that Eve has finite-time quantum memory \cite{lupo2015Entropy} in order to preserve composable security required for QKD \cite{muller2009composability}). Thus, this represents a strong form of quantum private-key cryptography, requiring only very short keys compared to the message length.

Since then, quantum data locking has found its application for Boson Sampling \cite{huang2019boson}. 
However, the scheme is very challenging to implement on a large scale over long distances. Consider an optical implementation, where the message is photonically encoded. Now the scheme represents a complex, multi-mode, generalised Mach-Zehnder interferometer\index{Mach-Zehnder (MZ) interference}, meaning that the channel between Alice and Bob, who might be far apart, must be interferometrically stabilised\index{Interferometric!Stability} (Sec.~\ref{sec:opt_stab}) on the order of the photons' wavelength (hundreds of nanometers for optical frequencies), which is extremely challenging over long distances.

@@
